### 2016-11-07 text/ms.Rmd
Add a ,

More broadly, in ecology 
predictions about extinction risk are widely used at national (e.g., the US
Endangered Species Act and the Canadian Species at Risk Act) and international
[e.g., the IUCN Red List, @iucn2015] levels. These risk assessments generally
involve fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g., @anderson2011a; @pinsky2011], or fitting
population-dynamic models to data for individual species [e.g., @dfo2010]. Both
types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk [e.g., coefficient
averaging, @burnham2002; generalized modeling, @yeakel2011; or semi-parametric
methods, @thorson2014], ensemble methods are a relatively simple way to combine
predictions in a transparent manner. Beyond estimates of status and trend,
ensemble methods could be used, for example, to increase the robustness of
spatial predictions when designing networks of protected areas
[@rassweiler2014] or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].
In any case, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which they are calibrated.

>>>>

More broadly, in ecology, 
predictions about extinction risk are widely used at national (e.g., the US
Endangered Species Act and the Canadian Species at Risk Act) and international
[e.g., the IUCN Red List, @iucn2015] levels. These risk assessments generally
involve fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g., @anderson2011a; @pinsky2011], or fitting
population-dynamic models to data for individual species [e.g., @dfo2010]. Both
types of models are prone to error caused by model-misspecification and
therefore results are sensitive to decisions about model structure
[@brooks2015]. Although there are options to account for potential
model-misspecification in determination of species risk [e.g., coefficient
averaging, @burnham2002; generalized modeling, @yeakel2011; or semi-parametric
methods, @thorson2014], ensemble methods are a relatively simple way to combine
predictions in a transparent manner. Beyond estimates of status and trend,
ensemble methods could be used, for example, to increase the robustness of
spatial predictions when designing networks of protected areas
[@rassweiler2014] or to forecast potential spatial shifts in species
distribution given climate impacts [@harsch2014].
In any case, superensembles are not a panacea 
and are ultimately limited by the quality, breadth, and representativeness
of simulated or trusted data to which they are calibrated.
